Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-03-04 manuscript/supplements_rsfmri.Rmd
Fraukes change in draft + supplement

## Aggregated FC: confirmatory analysis of an interaction effect of group and time 
```{r load agg FC data and prepare, echo=FALSE}
final_FC <- read.csv("../report/final_FC.csv")
final_FC$group_factor=relevel(final_FC$group_factor, "KG")
final_FC=merge(final_FC,subset(final_FC, tp=="bl",select=c("subj.ID", "BMI")), by='subj.ID')
colnames(final_FC)[27]="BMI.bl"
```

@@

<b>

>>>>

## Aggregated FC: confirmatory analysis of an interaction effect of group and time 
```{r load agg FC data and prepare, echo=FALSE}
final_FC <- read.csv("../report/final_FC.csv")
final_FC$group_factor=relevel(final_FC$group_factor, "KG")
```

@@
